---
title: "Info 201 students coding experience report"
output: html_document
---

```{r setup, include=FALSE}
library("dplyr")
library("ggplot2")
library("ggthemes")
library("ggmosaic")
library("plotly")
library("lintr")
library("stringr")
library("data.table")
source("scripts/chart_one.R")
source("scripts/chart_two.R")
source("scripts/summary.R")
data <- read.csv("data/intro-survey.csv", stringsAsFactors = FALSE)
data_list <- summarizing_data(data)
data <- data_list$modified_table
```

***
#Summary

From the survey data of **Info 201** class this quarter, we see that there are 
*`r data_list$total_students`* students in our Info201 class with different
experience with R, git and programming. From the data we see that
*`r data_list$no_exp_r`%* of students have never used R language before and 
*`r data_list$no_exp_git`%* of students have never used git before. There are 
also *`r data_list$no_exp_coding`%* of students with no programming experience.

In this report, we will investigate more about students' experience from the 
survey data using two plots.


***
#plot 1: coding experience by class standing

This first plot shows the coding experience of different class standings, from 
which we see that Sophomore is the **largest** group of students in this class. 
For every class standing, the number of experienced programmers _(with lots or_ 
_moderate coding experience)_ is more than half of the total number. Hence it 
would not be very surprising if students generally do a great job in this 
class. Besides, we see that sophomore is also the **largest** group of students 
with no programming experience.

`r chart_one_function(data_list$sorted_data, "class_standing",
                   "number_of_students", "coding_experience")`

***
#plot 2: git usage by coding experience

This second plot shows the git usage by coding experience.The **width** of each 
bar is proportional to the number of people with the corresponding coding 
experience. From this plot we see that most students have _never_ used git 
before. Even more than half of people with _moderate_ coding experience
have _never_ used git. Although _most_ students with lots of programming 
experience have used git in the past, students at this coding experience 
level are only a _small_ portion of the whole class.

```{r plot2, echo = FALSE}
chart_two_function(data)
```
